\textls[-0]{\thetitle}

### 2023-03-03 introduction.tex
kill two orphans

Language mechanisms including
mixins~\cite{mixin-1990},
virtual classes~\cite{virtualclasses-1989,vc-calculus-2006},
virtual types~\cite{thorup97}, % and associated types~\cite{ckj05},
extensible cases~\cite{bac2006}, etc.\ 
are all based on this essential idea of inheritance.
%
In particular, when a language mechanism allows late binding of the
meaning of nested types and terms,
it is said to support \emph{family polymorphism}~\cite{ernst2001family}:
types and terms are polymorphic to a family they are nested within.

>>>>

Language mechanisms including
virtual classes~\cite{virtualclasses-1989,vc-calculus-2006},
mixins~\cite{mixin-1990},
virtual types~\cite{thorup97}, % and associated types~\cite{ckj05},
and extensible cases~\cite{bac2006}
are based on this essential idea of inheritance.
%
In particular, when a language mechanism allows late binding of the
meaning of nested types and terms,
it is said to support \emph{family polymorphism}~\cite{ernst2001family}:
types and terms are polymorphic to a family they are nested within.

### 2023-03-03 metatheory-condensed.tex
kill two orphans

\TT is intended as a foundational model. So unlike our programmer-facing plugin,
%typing is structural rather than nominal\EDJ{I don't actually know what do you mean by structural here. I think surface syntax (Coq) is pretty structual as well.}, and
fields automatically axiomatized by the plugin require explicit definitions in \TT.
%
\TT provides MLTT-style constructs that can be used to express families and
family polymorphism. %rather than building it in directly.
%
Most notably, it extends MLTT with what we call \emph{linkages}.
(Linkages are a namesake of the theoretical device through which prior work~\cite{zm2017} models
family polymorphism in an OO setting, but the technical details differ significantly from the prior work.)

@@

\item
\TT also features \emph{linkage transformers}, used to model the features like inheritance, extending and overriding components in \Lang .
\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.

>>>>

\TT is intended as a foundational model. So unlike our programmer-facing plugin,
%typing is structural rather than nominal\EDJ{I don't actually know what do you mean by structural here. I think surface syntax (Coq) is pretty structual as well.}, and
fields automatically axiomatized by the plugin require explicit definitions in \TT.
%
\TT provides MLTT-style constructs that can be used to express families and
family polymorphism. %rather than building it in directly.
%
Most notably, it extends MLTT with what we call \emph{linkages}.
(Linkages are a namesake of the theoretical device through which \citet{zm2017} model
family polymorphism in an OO setting, but the technical details differ significantly from the prior work.)

@@

\item
\TT features \emph{linkage transformers}, which model how a family can be
inductively constructed by inheriting fields from another family,
adding new fields, and overriding existing fields.
\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.
